---
title: "Seloger Scraper"
output: html_notebook
---

*Get Pages*
This functions reads the web page given and returns the amount of pages of all the anounces in the link

```{r}
library(ScrapingSelonger)
library(rvest)
link<-"http://www.seloger.com/list.htm?idtt=2&naturebien=1,2,4&idtypebien=1,2&ci=750056&tri=initial&surfacemin=5&surfacemax=20"
Web_page<-read_html(link)
No_Pages<-GetPages(Web_page)
print(No_Pages)
```

*Creates DataFrame*
Takes the input link and downloads all the announces into a DataFrame

```{r}
library(ScrapingSelonger)
link<-"http://www.seloger.com/list.htm?idtt=2&naturebien=1,2,4&idtypebien=1,2&ci=750056&tri=initial&surfacemin=5&surfacemax=20"
Data<-CreatesDataframe(link)
```

*Fix Parameters*
Adjusts the scrapped data. Posibles inputs of Type (Cartier, Property, Area, Piece, Chambre)

```{r}
library(ScrapingSelonger)
link<-"http://www.seloger.com/list.htm?idtt=2&naturebien=1,2,4&idtypebien=1,2&ci=750056&tri=initial&surfacemin=5&surfacemax=20"
WEB_PAGE <- read_html(link)
PRE_CARTIER  <- WEB_PAGE %>% html_nodes(".c-pa-city") %>% html_text()
CARTIER <-FixParameters(PRE_CARTIER[1],"Cartier")
print(CARTIER)
```

*Clean Vector*
Adjusts the complete arry with FixParameters. Posibles inputs of Type (Cartier, Property, Area, Piece, Chambre, Price)

```{r}
library(ScrapingSelonger)
link<-"http://www.seloger.com/list.htm?idtt=2&naturebien=1,2,4&idtypebien=1,2&ci=750056&tri=initial&surfacemin=5&surfacemax=20"
WEB_PAGE <- read_html(link)
PRE_CARTIER  <- WEB_PAGE %>% html_nodes(".c-pa-city") %>% html_text()
CARTIER <-CleanVector(PRE_CARTIER,"Cartier")
print(CARTIER)
```

*Groups Area*
Set the areas in discrete groups

```{r}
library(ScrapingSelonger)
link<-"http://www.seloger.com/list.htm?idtt=2&naturebien=1,2,4&idtypebien=1,2&ci=750056&tri=initial&surfacemin=5&surfacemax=20"
WEB_PAGE <- read_html(link)
PRE_CARACT   <- WEB_PAGE %>% html_nodes(".c-pa-criterion") %>% html_text()
AREA      <- CleanVector(PRE_PRICE, "Area")
AREA_GROUP<- lapply(PRICE,GroupsArea)
print(AREA_GROUP)
```

*Groups Prices*
Set the prices in discrete groups

```{r}
library(ScrapingSelonger)
link<-"http://www.seloger.com/list.htm?idtt=2&naturebien=1,2,4&idtypebien=1,2&ci=750056&tri=initial&surfacemin=5&surfacemax=20"
WEB_PAGE <- read_html(link)
PRE_CARACT   <- WEB_PAGE %>% html_nodes(".c-pa-criterion") %>% html_text()
PRICE      <- CleanVector(PRE_PRICE, "Price")
PRICE_GROUP<- lapply(PRICE,GroupsPrice)
print(PRICE_GROUP)
```

*Download All Info of Paris*
Using the functions on the package is posible to download all the information of one city in Selonger.com

```{r}
library(ScrapingSelonger)
m = matrix(c(5,10,20,30,40,50,60,70,80,100,150,200,9,19,29,39,49,59,69,79,99,149,199,400), nrow=12, ncol=2)
links =NULL
for (i in 1:12)
{
  p1 <-"http://www.seloger.com/list.htm?idtt=2&naturebien=1,2,4&idtypebien=1,2&ci=750056&tri=initial&"
  p2 <- paste("surfacemin=",as.character(m[i,1]), sep="")
  p3 <- paste("&surfacemax=",as.character(m[i,2]), sep="")
  link=paste(paste(p1,p2, sep=""),p3, sep="")
  links=append(links, link)
}

#Loop through Areas
for (i in range(links))
{
  ScrapedData <-CreatesDataframe(links[i])
  if (i==1){
    ParisData<-ScrapedData
  } else {ParisData<-rbind(ParisData, ScrapedData)}
}
```

sometimes selonger.com identifies the web scrapin and blocks the user. That has been a problem when finishing the loop defined in the previous chunk.
